The Categorical Structure of Profunctor Optics

### 2017-11-10 paper.tex
Comment out proof that might not be relevant

\subsection{Equivalence of Optics}

One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle : S \hto A$ are equal. For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.

\todo{This may work in general with some huge number of conditions: something like $-A$ reflects monomorphisms and preserves binary coproducts, all subobjects in $\M$ have complements.}

\begin{proposition}
Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis. Then two lenses $\langle l, r \rangle$ and $\langle l', r' \rangle :  S \hto A$ with complements $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
\end{proposition}
\begin{proof}
The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.

%note that $p$ and $q$ must have identical $\fget$ and $\fput$ functions:
%\begin{align*}
%\fget &= \pi_2 l = \pi_2 l' \\
%\fput &= r (\pi_1 l \times A) = r' (\pi_1 l' \times A)
%\end{align*}
For the forward direction, note that the map $(\pi_1 l \times A)$ is a retraction: it has the section $(r, \pi_2)$:
\begin{align*}
(\pi_1 l \times A)(r, \pi_2) = (\pi_1 l r, \pi_2) = (\pi_1, \pi_2) = \id_{S \times A}
\end{align*}
Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$. The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.

The situation is summarised in the following diagram, which other than the dashed line, we know commutes.
\[
\begin{tikzcd}
M \times A \ar[r, "{f \times A}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{\pi_1 l' \times A}"] \ar[l, "{\pi_1 l \times A}", swap] & N \times A \ar[d, "r'"] \\
S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{[\id_S, \fget]}"] \ar[r, equal] & S \ar[d, "l'"] \\
M \times A & S \times A \ar[r] \ar[l] & N \times A
\end{tikzcd}
\]
We can now calculate:
\begin{align*}
r = r(\pi_1 l f \times A) = \fput (f \times A) = r' (\pi_1 l' f \times A) = r'(\phi \times A)
\end{align*}
as required. The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
\end{proof}

The conditions of the above Proposition hold in $\Set$, so long as $A$ is not empty.

>>>>

%\subsection{Equivalence of Optics}
%
%One issue with the definition of optic given in the last section is that it could be difficult to determine when two optics $\langle l, r \rangle, \langle l', r' \rangle : S \hto A$ are equal. For some choices of $\M$, however, we can reduce a zigzag of relations to a single one.
%
%\todo{This may work in general with some huge number of conditions: something like $-A$ reflects monomorphisms and preserves binary coproducts, all subobjects in $\M$ have complements.}
%
%\begin{proposition}
%Suppose all epimorphisms split in $\C$, and that $- \times A : \C \to \C$ reflects epis. Then two lenses $\langle l, r \rangle$ and $\langle l', r' \rangle :  S \hto A$ with complements $M$ and $N$ respectively are equal iff there exists an morphism $\phi : M \to N$ such that $(\phi \times A)l = l'$ and $r = r' (\phi \times A)$.
%\end{proposition}
%\begin{proof}
%The backward direction is clear: the morphism $\phi$ is a witness that $\langle l, r \rangle \rightsquigarrow \langle l', r' \rangle$, so the two optics are equal.
%
%%note that $p$ and $q$ must have identical $\fget$ and $\fput$ functions:
%%\begin{align*}
%%\fget &= \pi_2 l = \pi_2 l' \\
%%\fput &= r (\pi_1 l \times A) = r' (\pi_1 l' \times A)
%%\end{align*}
%For the forward direction, note that the map $(\pi_1 l \times A)$ is a retraction: it has the section $(r, \pi_2)$:
%\begin{align*}
%(\pi_1 l \times A)(r, \pi_2) = (\pi_1 l r, \pi_2) = (\pi_1, \pi_2) = \id_{S \times A}
%\end{align*}
%Now by assumption, $\pi_1 l : S \to M$ is an epi, so has a retraction $f : M \to S$. The claim is that $\phi = \pi_1 l' f$ is the required morphism $M \to N$.
%
%The situation is summarised in the following diagram, which other than the dashed line, we know commutes.
%\[
%\begin{tikzcd}
%M \times A \ar[r, "{f \times A}", dashed, bend left = 50] \ar[d, "r", swap] & S \times A \ar[d, "\fput"] \ar[r, "{\pi_1 l' \times A}"] \ar[l, "{\pi_1 l \times A}", swap] & N \times A \ar[d, "r'"] \\
%S \ar[r, equal] \ar[d, "l", swap] & S \ar[d, "{[\id_S, \fget]}"] \ar[r, equal] & S \ar[d, "l'"] \\
%M \times A & S \times A \ar[r] \ar[l] & N \times A
%\end{tikzcd}
%\]
%We can now calculate:
%\begin{align*}
%r = r(\pi_1 l f \times A) = \fput (f \times A) = r' (\pi_1 l' f \times A) = r'(\phi \times A)
%\end{align*}
%as required. The equation relating $l$ and $l'$ follows immediately as they are the inverses of $r$ and $r'$.
%\end{proof}
%
%The conditions of the above Proposition hold in $\Set$, so long as $A$ is not empty.
